Article title

### 2017-06-27 paper-webserver.tex
ADD: updates to the first two paras

The surveilance of bacterial pathogens is routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and many others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are being displaced by culture-independent methods based on whole-genome sequencing (WGS). Advances in WGS technologies have allowed the monitoring and sharing of outbreak data is real-time \cite{ronholm2016navigating}.

Subtyping software often requires command-line or programming experience. To make these \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.

Here we present Spfy, a platform, for bundling subtyping modules and machine-learning analyses, built using modern containerization, task queues, and exception handling.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text \cite{1}.

>>>>

The surveilance of bacterial pathogens is a routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are becoming displaced by culture-independent methods based on whole-genome sequencing (WGS). Secondary analyses, the study of relations and historical relevance of genomes, are now possible on large datasets through WGS \cite{ronholm2016navigating}. Advances in WGS technologies have also enabled the monitoring and sharing of outbreak information in real-time \cite{ronholm2016navigating}.

Subtyping and other analyses software often requires command-line or programming experience. To make these \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Canada \cite{whiteside2016superphy} and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.

Here we present Spfy, a platform for bundling subtyping modules and machine-learning predictions, built using modern containerization of services, task queues for parrelelizing analyses, and exception handling throughout.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text{}. Text.
Text \cite{1}.
